A large-scale analysis of racial disparities in police stops across the

### 2019-07-29 lib/paper_results.Rmd
Update to match paper text

>>>>

State patrol agencies analyzed: 
`r disp$state$outcome$results$hit_rates$geography %>% unique()`
Number of state patrol searches: 
`r disp$state$outcome$results$hit_rates$n_search_conducted %>% sum()`
Municipal departments analyzed:
`r disp$city$outcome$results$hit_rates$geography %>% unique()`
Number of municipal pd searches: 
`r disp$city$outcome$results$hit_rates$n_search_conducted %>% sum()`
